\section{What are Spheres}
In this section we want to inspect representations of homotopical Spheres. To give a little overview we will define the sphere to come with an orientation. To be more specific we have the definition:
\begin{definition}[The $k-$-Sphere]
	Let $\R^k$ be the k-dimensional vector space given as the span of $e_1,\dots e_k$ together with the eucliden metric $\norm{\cdot}_2$. Then the set
	\begin{align*}
		S^k\coloneq \{x\in \R^k|\norm{x}_2=1 \}
	\end{align*} is called the \textbf{$k-$sphere}.
\end{definition} This sphere will be our save haven where we will always come back to. In this definition there is no room for "diffrent orientations on a sphere". In our reality we will detect the two  "different orientations" of a space $A$ homotopic to a sphere that arise from two constructions as follows: assume that $\alpha$ and $\beta$ are the maps $A\to S^k$. then there is an endomorphism $f: S^k\to S^k$ such that our diagramm commutes:
\begin{center}
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZARgBoAGAXVJADcBDAGwFcYkQBBEAX1PU1z5CKAEyli1Ok1bsAygD0A1jz4gM2PASLlxkhizaIQC5d0kwoAc3hFQAMwBOEALZIdIHBCRkpB9gB1-ACMYHHoVeydXRHdPJDFfGSNApjQAC3CaRnoQxgAFAU1hEAcsSzScCJBHF3iaOMQffSTqnkpuIA
\begin{tikzcd}
	& A \arrow[rd, "\beta"] \arrow[ld, "\alpha"'] &     \\
	S^k \arrow[rr, "f"] &                                             & S^k
\end{tikzcd}
\end{center}
 Now $f^*:K^n(S^k)\to K^n(S^k)$ is an isomorphism and hence either the identity or minus the identity.
 
 
Now we have a lot of spaces that are homotopic or even homeomorph to the sphere. Just to name a view constructions:
\begin{enumerate}
	\item The disc in $\R^k$ modulo its boundary $D^k\slash \partial D^k$.
	\item The cone over the boundary of a $D^k$ disc. 
	\item The resduced and unreduced susopension of a $k-1$ sphere. 
	\item The one-point compactification of a vector space together with an oriented basis.
\end{enumerate}
We already saw how we can map the one-point compactification of a vector space with an ordered basis to a sphere wia the stereographic projections from the south pole. 
So lets inspect the other construction
\begin{cor}
	Given the disk $D^k\subseteq \R^k$ we have a homeomorphism 
	\begin{align*}
		\overline{D^k} \slash \partial D^k\to S^k
	\end{align*}
\end{cor}
\begin{proof}
	We will construct a proper map from the open disk to $R^k$ and by this we get a homeomorphism between their one-point-compaktifications.
	\begin{align*}
		s: D^k&\to \R^k\\
			x &\mapsto x \cdot \frac{1}{1-\norm{x}_2}
	\end{align*}
	This is a homeomorphism and proper. Hence, we get a map between the onepoint compactifications
	\begin{align*}
		\overline{D^k}\slash \partial D^k \to \R^k\cup \{\infty\}
	\end{align*} and the latter is homeomorphic to the Sphere. 
\end{proof}
\begin{cor}
Let $\overline{D^k}\cup C \partial D^k$ be the cone over the boundary of the disk. This is homeomorphic to the $k-$sphere. 
\end{cor}
\begin{proof}
	Again we will use the language of onepoint compactifications. First we give a homeomorphism from the "open cone" over the boundary to the open disc. To do this we include our space into $R^k$ as follows:
	\begin{align*}
	f:	\overline{D^k}\cup \partial D^k \times [0,1) &\to R^{k}\\
		x								 &\mapsto
		 \left\{ \begin{array}{ll}
		 	x & \text{if } x \in \overline{D^k} \, , \\
		 	(1+t)x& \text{if } (x,t)\in \partial D^k \times [0,1) \, . 
		 \end{array}
		 \right.
	\end{align*} This is a homeomorphism (if we restrict the image to $\{x\in R^k| \norm{x}_2<2\})$. This can be seen as follows:
	Obviously it is bijective and the contiuouty can be derived from the gluing lemma. To see the contiuoity of the invese we can explicitly describe it:
\begin{align*}
	f^{-1}: \{x\in R^k| \norm{x}_2<2\}  &\to    \overline{D^k}\cup \partial D^k \times [0,1) \\
	x 									&\mapsto \left\{ 
	\begin{array}{ll}
		x & \text{ if } x\in \overline{D^k} \,,  \\
		(\frac{x}{\norm{x}_2},(1-\norm{x}_2)) & \text{ if } \norm{x}_2\geq 1 \,,
	\end{array}
	\right.
\end{align*}
\end{proof}
